Compiling refinement types to dependent types

### 2020-07-05 tex/paper.tex
State the theorem
Add some TODOs to ensure I don't forget about them

@@

We translate the surface language types and terms using the $\mu_\tau$ and $\mu_\varepsilon$ functions respectively.
$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)  \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}  \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))          \\
  & \mu_\tau( \nonterm{es} )                                    && \triangleq \mu_\varepsilon(\nonterm{es}) = \text{True}                 \\
  & \mu_\tau(B)                                                 && \triangleq B                                                           \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements (which are $\text{Bool}$-typed terms) are translated to propositions stating that the corresponding term is equal to $\text{True}$,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

>>>>

%TODO describe the notion of the oracle (like an SMT solver) and what we expect of the oracle.

@@

We translate the surface language types and terms using the $\mu_\tau$ and $\mu_\varepsilon$ functions respectively.
$\mu_\tau$ is defined as follows:
\begin{equation}
\begin{aligned}
  & \mu_\tau( (x : \nonterm{ts}_1) \rightarrow \nonterm{ts}_2)  && \triangleq \Pi x : \mu_\tau(\nonterm{ts}_1). \mu_\tau(\nonterm{ts}_2)  \\
  & \mu_\tau( \{ v : \nonterm{ts} | \nonterm{r} \})             && \triangleq \{ v : \mu_\tau(\nonterm{ts})\ **\ \mu_\tau(\nonterm r) \}  \\
  & \mu_\tau( \nonterm r_1 \land \nonterm r_2 )                 && \triangleq ( \mu_\tau(\nonterm r_1) , \mu_\tau(\nonterm r_2))          \\
  & \mu_\tau( \nonterm{es} )                                    && \triangleq \mu_\varepsilon(\nonterm{es}) = \text{True}                 \\
%TODO add syntax/typing rules for True
  & \mu_\tau(B)                                                 && \triangleq B                                                           \\
\end{aligned}
\end{equation}
Or, in words:
\begin{itemize}
  \item (dependent) arrow types are translated to the corresponding $\Pi$-types,
  \item refined types are translated to the corresponding $\Sigma$-types,
  \item atomic refinements (which are $\text{Bool}$-typed terms) are translated to propositions stating that the corresponding term is equal to $\text{True}$,
  \item conjunctions of several (atomic) refinements are represented as tuples of the corresponding atomic translations.
\end{itemize}

%TODO define translation for gammas

\subsection{Correctness}

We next formulate our key theorem:

\theorem For any well-typed surface language term $\nonterm{es}$, the result of the translation $\mu_\epsilon(\nonterm{es})$ is well-typed in the core language:
\[
  \nonterm G \vdash \nonterm{es} : \nonterm{ts} \implies \mu_\Gamma(\nonterm G) \vdash \mu_\epsilon(\nonterm{es}) : \mu_\tau(\nonterm{ts})
\]
